\documentclass{article}

\title{Test Cases}
\author{Alireza Dastmalchi Saei}
\date{\today}

\begin{document}

\maketitle

\section{Introduction}

This is the introduction section of my document.

\pagebreak

\section{Test Scenario 1: City and Train Management}
\bigskip
\bigskip
\subsection{Test Case 1.1: Add a New City}

\textbf{Description:} Verify that a new city can be added to the system.\\
\textbf{Preconditions:}
\begin{itemize}
  \item The system is running.
  \item The user is authorized to add a new city.
\end{itemize}
\textbf{Steps:}
\begin{enumerate}
  \item Add a new city.
\end{enumerate}
\textbf{Expected Result:} The city should be added to the list of cities in the system.

\bigskip
\hrule
\bigskip


\subsection{Test Case 1.2: Add a New Train}

\textbf{Description:} Verify that a new train can be added to the system.\\
\textbf{Preconditions:}
\begin{itemize}
  \item The system is running.
  \item The user is authorized to add a new train.
\end{itemize}
\textbf{Steps:}
\begin{enumerate}
  \item Add a new train.
\end{enumerate}
\textbf{Expected Result:} The new train should be added to the list of trains in the system.

\pagebreak

\section{Test Scenario 2: Trip Management}
\bigskip
\bigskip
\subsection{Test Case 2.1: Create a New Trip}

\textbf{Description:} Verify that a new trip can be added to the system considering the specific constraints.\\
\textbf{Preconditions:}
\begin{itemize}
  \item The system is running.
  \item The user is authorized to add a new trip.
\end{itemize}
\textbf{Steps:}
\begin{enumerate}
  \item Provide valid details for the new trip: Origin
  \item Provide valid details for the new trip: Destination
  \item Provide valid details for the new trip: Train
  \item Provide valid details for the new trip: Departure Time
  \item Provide valid details for the new trip: Arrival Time
\end{enumerate}
\textbf{Expected Result:} The new trip should be created and registered in the system.

\bigskip
\hrule
\bigskip

\subsection{Test Case 2.2: Cancel Trip}

\textbf{Description:} Verify that a trip can be canceled in the system.\\
\textbf{Preconditions:}
\begin{itemize}
  \item The system is running.
  \item The user is authorized to cancel a trip.
\end{itemize}
\textbf{Steps:}
\begin{enumerate}
  \item Select a trip to cancel 
\end{enumerate}
\textbf{Expected Result:} The selected trip should be canceled, and all associated tickets should also be canceled.

\end{document}
